Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/results.tex
add random
finalize result of validation in RQ1

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this subproject, we used the review history from May 25, 2011 to June 13, 2012, which contains 6,605 changes and 72,484 comments.

@@

\textbf{Validation:} We validated our approach using bootstrapping cross validation. We randomly selected 90\% of 318 comments for training set and determine thresholds. We then applied the constructed model on the remaining 10\% comments as the validation set.
The performance on the validation sets was measured using precision, recall and F-measure.
This validation was repeated for 300 times to estimate the performance of our models.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure. The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately. This is better results than random model which achieved only XX\% of precision and YY\% of recall. \pick{Giving a random model as a base line would be easily to determine the performance of our models.}

@@

\begin{table}[!t]
\caption{Results from bootstrapping cross validation of our classification models}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccc|cc|cc}
\hline
Classifcation & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c}{F-measure} \\ \cline{2-7}
Models & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
$\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089\\
$\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118\\
\hline
\end{tabular}
\label{tb:xvalidate}
\end{table}

>>>>

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this subproject, we used the review history from May 2011 to June 2012, which contains 6,605 changes and 72,484 comments.

@@

\begin{table*}[!t]
\caption{Results from bootstrapping cross validation of our classification models against random models}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{cccc|cc|cc}
\hline
\multicolumn{2}{c}{Classifcation}   & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c}{F-measure} \\ \cline{3-8}
\multicolumn{2}{c}{Models} & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
\multirow{2}{*}{Useful} & $\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089\\ \cline{2-8}
& Random     &  0.421 & 0.114 &  0.376 & 0.116 & 0.496 & 0.144\\ \hline
\multirow{2}{*}{Useless}  & $\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118\\ \cline{2-8}
& Random    &  0.336 & 0.131 &  0.269 & 0.115 & 0.478 & 0.182\\
\hline
\end{tabular}
\label{tb:xvalidate}
\end{table*}

\textbf{Validation:} We validated our approach using bootstrapping cross validation. We randomly selected 90\% of 318 comments for training set and determine thresholds. We then applied the constructed model on the remaining 10\% comments as the validation set.
The performance on the validation sets was measured using precision, recall and F-measure.
This validation was repeated for 300 times to estimate the performance of our models.
For a baseline of our models, we determined the performance of the random models using same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure. The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately. Moreover, our models also achieved higher results than the random models twice for both precision and recall.

@@
